Title

### 2020-12-14 documents/DraftReport.Rmd
small edits to scenarios and estimation/diagnostics sections

Metrics to monitor  
CV (precision)  
RMSE (accuracy)  
Relative bias

Vary data quantity/combinations and demographic rates  
Low MR detection vs high  
Low daily nest survival vs high  
Low abund detection vs high

Best scenario, using all three datasets  
Potential add-on: vary life history traits:  
Survival: 0.3 vs. 0.8  
Fecundity: 0.3 vs. 0.5  
Remove nest monitoring entirely - use other two datasets (MR and counts)  
Model adjustments: informed priors?   
Sensitivity to priors?  
Remove MR data entirely - use other two datasets (nest monitoring and counts)  
Model adjustments: informed priors?  
Sensitivity to priors?   
Poorer quality MR  
Quantity: decrease N (20 individuals vs. 100 resights per year)  
Quality: decrease p (0.1, 0.5, 0.8) or annual surveys (5 vs. 10)

*Estimation and diagnostics*   
Nimble; iterations, burn-in, etc  
Examined relative bias, RMSE, etc

@@

Abadi, F., Gimenez, O., Arlettaz, R., Schaub, M., 2010. An assessment of integrated population models: bias, accuracy, and violation of the assumption of independence. Ecology 91, 7–14. https://doi.org/10.1890/08-2235.1

@@

>>>>

<!-- amelia - maybe easiest to create table in word doc when we also add figures? -->

<!-- amelia - I think these are all old notes? -->
<!-- Metrics to monitor   -->
<!-- CV (precision)   -->
<!-- RMSE (accuracy)   -->
<!-- Relative bias   -->

<!-- Vary data quantity/combinations and demographic rates   -->
<!-- Low MR detection vs high   -->
<!-- Low daily nest survival vs high   -->
<!-- Low abund detection vs high   -->

<!-- Best scenario, using all three datasets   -->
<!-- Potential add-on: vary life history traits:   -->
<!-- Survival: 0.3 vs. 0.8   -->
<!-- Fecundity: 0.3 vs. 0.5   -->
<!-- Remove nest monitoring entirely - use other two datasets (MR and counts)   -->
<!-- Model adjustments: informed priors?    -->
<!-- Sensitivity to priors?   -->
<!-- Remove MR data entirely - use other two datasets (nest monitoring and counts)   -->
<!-- Model adjustments: informed priors?   -->
<!-- Sensitivity to priors?    -->
<!-- Poorer quality MR   -->
<!-- Quantity: decrease N (20 individuals vs. 100 resights per year)   -->
<!-- Quality: decrease p (0.1, 0.5, 0.8) or annual surveys (5 vs. 10)   -->

*Estimation and diagnostics*   
<!-- amelia - just a quick draft, but is this right? -->
Models were ran in NIMBLE using program R (NIMBLE 2020). We ran 45,000 iterations with the first 5,000 as a burn-in. We thinned samples to reduce autocorrelation and retained every 10th sample, for a total of 4,000 samples. Model convergence was assessed visually using trace plots.

Examined relative bias, RMSE, etc

@@

Abadi, F., Gimenez, O., Arlettaz, R., Schaub, M., 2010a. An assessment of integrated population models: bias, accuracy, and violation of the assumption of independence. Ecology 91, 7–14. https://doi.org/10.1890/08-2235.1

@@

NIMBLE Development Team. 2020. NIMBLE: MCMC, Particle Filtering, and Programmable Hierarchical Modeling.  doi: 10.5281/zenodo.1211190. R package version 0.10.1, https://cran.r-project.org/package=nimble.
